### 2021-01-12 manuscript.tex
added space tree fig; updated file tree fig
resolved seafile conflict
improved formatting consistency across figs; add color reference to file_tree

% Packages and some formatting
\usepackage{titlesec,hyperref,booktabs,relsize,setspace,float,verbatim,caption,subcaption,graphicx}
\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue}
%\hypersetup{hidelinks}
\titleformat{\chapter}[hang]
{\normalfont\huge\bfseries}{\chaptertitlename\ \thechapter:}{1em}{}
\doublespacing{}
\setcounter{tocdepth}{1}

@@

\begin{figure}[H]
    \includegraphics[width=\linewidth]{figs/rmarkdownflow.png}
    \caption{[TEMP] Rmarkdown Rendering Flow}\label{fig:renderFlow}
\end{figure}

@@

\begin{figure}
\centering
    \addtolength\tabcolsep{-0.2em}
    \relsize{-2}
\begin{subfigure}[b]{.5\linewidth}
    \centering
\begin{verbatim}
name: "Candidate Cancer Gene Database"
navbar:
    title: "CCGD"
    left:
        - text: "Home"
          href: index.html
        - text: "Search"
          href: search.html
        - text: "Help"
          href: help.html
        - text: "References"
          href: references.html
        - text: "Contact"
          href: contact.html
\end{verbatim}
\caption{\_site.yml: file for site assembly}\label{fig:siteYaml}
\end{subfigure}%
\begin{subfigure}[b]{.5\textwidth}
\centering
\begin{verbatim}
---
title: "Candidate Cancer Gene Database"
bibliography: refs/ccgd_paper.bib
nocite: '@*'
output:
    html_document:
        includes:
            in_header: "styles/favicon.html"
            after_body: "styles/footer.html"
        css: styles/styles.css
        theme: readable
---
\end{verbatim}
\subcaption{index.Rmd individual page header}\label{fig:pageHeader}
\end{subfigure}
\caption{YAML Configuration Code Segments}\label{fig:yamls}
    \addtolength\tabcolsep{+0.2em}
    \relsize{+2}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{figs/g238.png}
    \caption{table\_app/app.R Reactive Graph}\label{fig:reactiveGraph}
\end{figure}

@@

@@

>>>>

% Packages and some formatting
\usepackage{titlesec,hyperref,booktabs,relsize,setspace,float,verbatim,caption,subcaption,graphicx}
%\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue}
\hypersetup{hidelinks}
\titleformat{\chapter}[hang]
{\normalfont\huge\bfseries}{\chaptertitlename\ \thechapter:}{1em}{}
\doublespacing{}
\setcounter{tocdepth}{1}

@@

\begin{figure}[H]
    \includegraphics[width=\linewidth]{fig/rmarkdown_flow.png}
    \caption{Rmarkdown Rendering Flow}\label{fig:renderFlow}
\end{figure}

@@

\begin{figure}
\centering
    \addtolength\tabcolsep{-0.2em}
    \relsize{-2}
\begin{subfigure}[b]{.5\linewidth}
    \centering
\begin{verbatim}
name: "Candidate Cancer Gene Database"
navbar:
    title: "CCGD"
    left:
        - text: "Home"
          href: index.html
        - text: "Search"
          href: search.html
        - text: "Help"
          href: help.html
        - text: "References"
          href: references.html
        - text: "Contact"
          href: contact.html
\end{verbatim}
\caption{\_site.yml: file for site assembly}\label{fig:siteYaml}
\end{subfigure}%
\begin{subfigure}[b]{.5\textwidth}
\centering
\begin{verbatim}
---
title: "Candidate Cancer Gene Database"
bibliography: refs/ccgd_paper.bib
nocite: '@*'
output:
    html_document:
        includes:
            in_header: "styles/favicon.html"
            after_body: "styles/footer.html"
        css: styles/styles.css
        theme: readable
---
\end{verbatim}
\subcaption{index.Rmd individual page header}\label{fig:pageHeader}
\end{subfigure}
\caption{YAML Configuration Segments}\label{fig:yamls}
    \addtolength\tabcolsep{+0.2em}
    \relsize{+2}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{fig/reactive_graph.png}
    \caption{table\_app/app.R Reactive Graph}\label{fig:reactiveGraph}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{fig/file_tree.png}
    \caption{Project directory file tree comparison}\label{fig:fileTree}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{fig/space_tree.png}
    \caption{Treemap of Disk Use Between App Versions}\label{fig:spaceTree}
\end{figure}

Ref crossdirstat
